Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-05-12 Manuscript/proto-manuscript.tex
Change in the reasoning for f_sigma value.

ECC and solvation $\Delta G$.(from \cite{Leontyev2015}: hydration $\Delta G$ can provide good structure and energetics, but will fail in good interactions -- already proved for cations)
In addition, $\Delta G_{hyd}$ -- the usual target for parametrization of small molecules in classical force fields -- is not the right target in the MDEC/ECC framework -- part of $\Delta G$ is already included in the polarization of electrons, and only the remining part of $\Delta G$ belongs to the polarization of the nuclei. 
Interestingly, the part of $\Delta G$ due to electrons is approximately $1/2$ of it, which is what I observe in my simulations -- if I assume that half of this energy is already accounted for by the water model (which is rather a MDEC model already), than I should recover approximately $3/4$ of the original interaction energy. 
When I write the formula for interaction energy for two particles at a distance $r=\sigma$ (approximate equilibrium position), I get
\begin{equation}
W(f_\sigma r,f_q q) = \kappa \frac{q_i q_j}{r} \frac{f_q^2}{f_\sigma}
\end{equation}

When I apply $3/4$-assumption for the intereaction energy, I require: 
\begin{equation}
\frac{3}{4} W(r,q) = W(f_\sigma r, f_q q)
\end{equation}

So for $f_q=0.8$ I obtain $f_\sigma ~= \frac{4}{3} f_q^2 \,\,\, = 0.853$ -- which is very close to the value I use, $f_\sigma=0.875$. This is a crude derivation neglecting the true position of energy minimum and the LJ mixing rules. However, the formula for $f_\sigma$ does not depend on the absolute position and I believe that the assumption that the minimum is relatively shifted by scaling with $f_\sigma$ holds pretty well.

>>>>

ECC and solvation $\Delta G$.(from \cite{Leontyev2015}: hydration $\Delta G$ can provide good structure and energetics, but will fail in good interactions -- already proved for cations)
In addition, $\Delta G_{hyd}$ -- the usual target for parametrization of small molecules in classical force fields -- is not the right target in the MDEC/ECC paradigm -- part of $\Delta G$ is already included in the polarization of electrons, and only the remining part of $\Delta G$ belongs to the polarization of the nuclei. 
Hence it is non trivial, how large should be the scaling factor $f_\sigma$ -- it should lay between $1$ and $f_q$, the limits for the original interaction energy and its limit when we neglect the $\Delta G_{el}$ term in $\Delta G_{hyd}$.
